Aa Language Reference Manual

### 2013-09-23 v2/Ahir-asm/devel/docs/AaLRM.tex
Document updated.

The \Aa language provides a single construct for describing loops.
The form of the construct is
\begin{verbatim}
  $dopipeline
     $merge $entry $loopback
       <phi-statements>
     $endmerge
     atomic-statement-sequence
  $while <condition-expression>
\end{verbatim}
The do-while statement can appear only in branch-blocks.  Control enters
the do-while from a predecessor in the branch-block, and stays in the
do-while as long as the condition-expression is false.  The \$loopback
place is used to repeat the loop-body.  The leading merge statement
in the do-while is used to merge the control-flow coming in either from
the entry to the do-while or from the loopback place.

@@

@@

Thus, an \Aa program is constructed as a collection of modules,
each of which is a sequence of statements.  The use of series,
parallel, fork and branch block
statements enables the programmer to describe a highly concurrent
structured system with complex branching behaviour.  
The resulting control flow structure is a
petri-net with provable liveness and safety properties \cite{ref:SameerPhD}.

>>>>

The \Aa language provides a single construct for describing loops.
The form of the construct is
\begin{verbatim}
  $dopipeline
     $merge $entry $loopback
       <phi-statements>
     $endmerge
     atomic-statement-sequence
  $while <condition-expression>
\end{verbatim}
The do-while statement can appear only in branch-blocks.  Control enters
the do-while from a predecessor in the branch-block, and stays in the
do-while as long as the condition-expression is false (the test is done
every time the loop body has finished).  The \$loopback
place is used to repeat the loop-body.  The leading merge statement
in the do-while is used to merge the control-flow coming in either from
the entry to the do-while or from the loopback place.

@@

Additionally, it is possible to specify that the loop-pipelining
be done to its extreme possibility, that is, to the maximum possible
rate that can be achieved.
\begin{verbatim}
  $dopipeline $depth 8 $buffering 2
  $fullrate // specify that extreme pipelining 
	    // should be attempted.
    ...
  $while ....
\end{verbatim}

@@

To summarize, an \Aa program is constructed as a collection of modules,
each of which is a sequence of statements.  The use of series,
parallel, fork and branch block
statements enables the programmer to describe a highly concurrent
structured system with complex branching behaviour.  
The resulting control flow structure is a
petri-net with provable liveness and safety properties \cite{ref:SameerPhD}.
